Interpolate the weight at agecl output to annual age

### 2020-06-04 InterpolateWeightAtAge.Rmd
adding diagnostics for species

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "survObsWtAtAge.rds")))
wtage <- wtage[[1]]

@@

```{r interpolate-wtage}
# a function to go into atlantisom, sketched here, reuse calc_stage2age as possible

wtagecl <- wtage
annages <- NOBAom_cod$truenumsage_ss %>%
  group_by(species, time, agecl) %>%
  rename(trueage = agecl) %>%
  summarise(truenatage = sum(atoutput))

@@

```{r omdimensions-bugfix}

@@

@@

Fix multispecies bug in om_index function:
```{r omindex-bugfix}

@@

Try om_comps step again:

```{r comps-redo}

@@

>>>>

wtage <- readRDS(file.path(d.name, paste0(scenario.name, "survObsWtAtAge.rds")))
wtage <- wtage[[1]] %>%
  filter(species == "North_atl_cod")

@@

```{r interpolate-wtage-dev}
# a function to go into atlantisom, sketched here, reuse calc_stage2age as possible

wtagecl <- wtage
annages <- NOBAom_cod$truenumsage_ss %>%
  filter(species == "North_atl_cod") %>%
  group_by(species, time, agecl) %>%
  rename(trueage = agecl) %>%
  summarise(truenatage = sum(atoutput))

@@

```{r omdimensions-bugfix, eval=FALSE}

@@

New omdimensions file:
```{r, code = readLines("./config/omdimenstions.R"), eval=F}
```

@@

Fix multispecies bug in om_index function:
```{r omindex-bugfix, eval=FALSE}

@@

Try om_comps step again (now works by allowing NA in max comparison of `calc_age2length()`:

```{r comps-redo, message=FALSE}

@@

What do the interpolated weight at ages look like? Diagnostic plots from function look the same as above for cod (good), blank for Capelin (good? didnt need extrapolation but may have other problems), and bad for Redfish between true ages 2-15; lots of overestimation.

```{r vis-interpolate-1, warning=FALSE}

# plot portion, just redfish, capelin is blank and cod looks the same
library(ggforce)
NOBAom_redcodcap_comp$survObsFullWtAtAge[[1]][[2]] + facet_wrap_paginate(~species, ncol=1, nrow = 1, page=3, scales = "free")

Compare ObsWtAtAge with ObsFullWtAtAge outputs by species:

```{r vis-interpolate-2}

# dataframe portion
intwtCod <- NOBAom_redcodcap_comp$survObsFullWtAtAge[[1]][[1]] %>%
  filter(species == "North_atl_cod")

intwtRed <- NOBAom_redcodcap_comp$survObsFullWtAtAge[[1]][[1]] %>%
  filter(species == "Redfish")

intwtCap <- NOBAom_redcodcap_comp$survObsFullWtAtAge[[1]][[1]] %>%
  filter(species == "Capelin") #empty

wtageCod <- NOBAom_redcodcap_comp$survObsWtAtAge[[1]] %>%
  filter(species == "North_atl_cod")

wtageRed <- NOBAom_redcodcap_comp$survObsWtAtAge[[1]] %>%
  filter(species == "Redfish")

wtageCap <- NOBAom_redcodcap_comp$survObsWtAtAge[[1]] %>%
  filter(species == "Capelin")

# handmade plots:

wtagecl <- wtageCap

  wtagep <- ggplot(wtagecl, aes(agecl, atoutput)) +
    geom_point() +
    geom_line(aes(colour = factor(time))) + 
    scale_x_continuous(minor_breaks = c(0:max(agecl))) +
    theme_tufte() +
    theme(legend.position = "none",
          panel.grid.minor.x = element_line(colour = "grey50"),
          panel.grid.major.x = element_line(colour = "grey50"))
